---
title: "Tweet level morality, stance, sentiment"
author: "Meltem Ozcan"
date: "2023-12-08"
output: pdf_document
---

```{r warning = FALSE, message=FALSE}
library(dplyr)
library(lubridate)
library(ggplot2)
library(glmmTMB)
library(dplyr)
library(tidyr)
```

```{r warning = FALSE, m/essage = FALSE}
dat <- readr::read_csv("/Users/meltemozcan/Desktop/PSYC 626/TwitterAbortion/Data/final_wave2_upd.csv")
# total tweets by each author over the full time period
total_num_tweets_per_auth <- dat %>% 
    group_by(author.id) %>% 
    summarise(num_tweets_by_author = n_distinct(id)) %>% 
    arrange(desc(num_tweets_by_author)) 
#total_num_tweets_per_auth %>% head()
#summary(total_num_tweets_per_auth$num_tweets_by_author)

length(unique(dat$author.id)) #72305 unique authors
length(unique(dat$id)) #245891 unique records
```

```{r}
dat$sentiment = ordered(as.factor(dat$sentiment), 
                        c("negative", "neutral", "positive"))
dat$prolife_prochoice <- ordered(as.factor(dat$prolife_prochoice),
                                 c("life", "neutral", "choice"))
dat$binary_morality <- ordered(as.factor(dat$binary_morality),
                               ordered(c("moral", "non-moral")))
dat$care <- ordered(as.factor(dat$care),
                               ordered(c("0", "1")))
dat$fairness <- ordered(as.factor(dat$fairness),
                               ordered(c("0", "1")))
dat$authority <- ordered(as.factor(dat$authority),
                               ordered(c("0", "1")))
dat$loyalty <- ordered(as.factor(dat$loyalty),
                               ordered(c("0", "1")))
dat$purity <- ordered(as.factor(dat$purity),
                               ordered(c("0", "1")))
dat$windows <- ""
dat[dat$pre52_Dobbs==1, "windows"] <- "pre-Dobbs"
dat[dat$btwn52_Dobbs_Overturn==1, "windows"] <-  "post-Dobbs & pre-overturn"
dat[dat$post52_Overturn==1, "windows"]<- "post-overturn"
dat$windows <- ordered(as.factor(dat$windows), 
                       c("pre-Dobbs", "post-Dobbs & pre-overturn", "post-overturn"))
```
 

```{r}
dat %>% group_by(binary_morality) %>% 
  summarise(n = n()) %>% mutate(prop = n/sum(n))
#0.429605 moral, 0.570395 nonmoral
```

```{r}
 dat %>% group_by(prolife_prochoice) %>% 
  summarise(n = n()) %>% mutate(prop = n/sum(n)) 
```



```{r}
choice <- dat[dat$prolife_prochoice == "choice",]
choice %>% group_by(binary_morality) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
choice %>% group_by(care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
choice %>% group_by(fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
choice %>% group_by(authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
choice %>% group_by(loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
choice %>% group_by(purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
```
```{r}
life <- dat[dat$prolife_prochoice == "life",]
life %>% group_by(binary_morality) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
life %>% group_by(care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
life %>% group_by(fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
life %>% group_by(authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
life %>% group_by(loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
life %>% group_by(purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
```

```{r}
neutral <- dat[dat$prolife_prochoice == "neutral",]
neutral %>% group_by(binary_morality) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
neutral %>% group_by(care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
neutral %>% group_by(fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
neutral %>% group_by(authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
neutral %>% group_by(loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
neutral %>% group_by(purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))
```

```{r}

```




```{r warning=FALSE, message=FALSE}
mft <- c( "care", "fairness", "authority", "loyalty", "purity")
p_pro_moral <- dat %>% group_by(prolife_prochoice, binary_morality) %>% 
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
  filter(binary_morality == "moral") %>% select(prop)

abortion <- c("pro-life", "neutral", "pro-choice")
p_pro_moral <- as.numeric(t(round(p_pro_moral[,2],3)))


p_pro_care <- dat %>% filter(binary_morality == "moral") %>%
  group_by(prolife_prochoice, care) %>% 
  summarise(n = n()) %>% mutate(prop = n/sum(n))
p_pro_care <- p_pro_care[c(2,4,6), ] %>% select(-c(n, care)) # rows where care == 1

p_pro_fair <- dat %>% filter(binary_morality == "moral") %>%
  group_by(prolife_prochoice, fairness) %>% 
  summarise(n = n()) %>% mutate(prop = n/sum(n))
p_pro_fair <- p_pro_fair[c(2,4,6), ] %>% select(-c(n, fairness))

p_pro_aut <- dat %>% filter(binary_morality == "moral") %>%
  group_by(prolife_prochoice, authority) %>% 
  summarise(n = n()) %>% mutate(prop = n/sum(n))
p_pro_aut <- p_pro_aut[c(2,4,6), ]%>% select(-c(n, authority))

p_pro_loyalty <- dat %>% filter(binary_morality == "moral") %>%
  group_by(prolife_prochoice, loyalty) %>% 
  summarise(n = n()) %>% mutate(prop = n/sum(n)) 

p_pro_loyalty <- p_pro_loyalty[c(2,4,6), ]%>% select(-c(n, loyalty))

p_pro_purity <- dat %>% filter(binary_morality == "moral") %>%
  group_by(prolife_prochoice, purity) %>% 
  summarise(n = n()) %>% mutate(prop = n/sum(n))
p_pro_purity <- p_pro_purity[c(2,4,6), ]%>% select(-c(n, purity))

mft_abortion <- cbind(rep(mft, each = 3), 
                      rbind(p_pro_care, 
                            p_pro_fair, 
                            p_pro_aut, 
                            p_pro_loyalty, 
                            p_pro_purity)) %>%
                  pivot_wider(names_from = prolife_prochoice,
                              values_from = prop)
mft_abortion <- rbind("moral" = p_pro_moral, mft_abortion)
mft_abortion <- as.data.frame(round(mft_abortion[,c(2:4)],3))
rownames(mft_abortion) <- c("moral", mft)
mft_abortion %>% kableExtra::kable()
```




## moral-nonmoral
```{r warning=FALSE, message=FALSE}
moral_p_PRE52 <- dat %>% group_by(pre52_Dobbs, binary_morality) %>%
    summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
   filter(binary_morality=="moral") 
# note can't interpret the window in between since it pools the beginning end of
# the year; not meaningful
moral_p_OV52 <- dat %>% group_by(post52_Overturn, binary_morality) %>%
    summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
   filter(binary_morality=="moral") 

moral_p_Bef <- dat %>% group_by(beforeOverturn, binary_morality) %>%
    summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
   filter(binary_morality=="moral") 
```

- pre52Dobbs (1 -> 0) 3% decrease in moral tweets

- post52Overturn (0 -> 1) 1% decrease

- beforeOverturn (1 -> 0) 5% decrease

## Care 
```{r warning=FALSE, message=FALSE}

care_p_PRE52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(pre52_Dobbs, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
   filter(care==1) 

care_p_OV52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(post52_Overturn, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
   filter(care==1) 

care_p_Bef<- dat %>% filter(binary_morality=="moral") %>%
  group_by(beforeOverturn, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
   filter(care==1) 
```


- pre52Dobbs (1 -> 0) prop tweets endorsing care decreased by about 8%

- post52Overturn (0 -> 1)  prop tweets endorsing care decreased by about 5%

- beforeOverturn (1 -> 0)   prop tweets endorsing care decreased by about 3%

## Authority

```{r warning=FALSE, message=FALSE}

aut_p_PRE52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(pre52_Dobbs, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
         filter(authority==1) 

aut_p_OV52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(post52_Overturn, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
         filter(authority==1) 

aut_p_Bef <- dat %>% filter(binary_morality=="moral") %>%
  group_by(beforeOverturn, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
         filter(authority==1) 
```

- pre52Dobbs (1 -> 0) ~1% increase

- post52Overturn (0 -> 1) ~2% decrease

- beforeOverturn (1 -> 0) ~ 1% increase

## Fairness

```{r warning=FALSE, message=FALSE}
fair_p_PRE52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(pre52_Dobbs, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
         filter(fairness==1) 

fair_p_OV52 <-dat %>% filter(binary_morality=="moral") %>%
  group_by(post52_Overturn, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
         filter(fairness==1)  

fair_p_Bef <-dat %>% filter(binary_morality=="moral") %>%
  group_by(beforeOverturn, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
         filter(fairness==1) 
```


- pre52Dobbs (1 -> 0) 7% increase

- post52Overturn (0 -> 1) 1% inc

- beforeOverturn (1 -> 0) 1% inc


## Loyalty

```{r warning=FALSE, message=FALSE}

loyal_p_PRE52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(pre52_Dobbs, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
   filter(loyalty==1) 

loyal_p_OV52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(post52_Overturn, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
      filter(loyalty==1) 

loyal_p_Bef <- dat %>% filter(binary_morality=="moral") %>%
  group_by(beforeOverturn, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
    filter(loyalty==1) 
```

- pre52Dobbs (1 -> 0) **10% increase**

- post52Overturn (0 -> 1) 1% inc

- beforeOverturn (1 -> 0) 6% inc


## Purity
 
```{r warning=FALSE, message=FALSE}
 pur_p_PRE52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(pre52_Dobbs, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
      filter(purity==1) 

pur_p_OV52 <- dat %>% filter(binary_morality=="moral") %>%
  group_by(post52_Overturn, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% 
       filter(purity==1)  

pur_p_Bef <- dat %>% filter(binary_morality=="moral") %>%
  group_by(beforeOverturn, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% 
       filter(purity==1) 
```

- pre52Dobbs (1 -> 0) 2% drop

- post52Overturn (0 -> 1) 1% drop

- beforeOverturn (1 -> 0) 0.sth no change


```{r include = FALSE}
#labs <- c("window", "moral", "care", "fairness", "authority", "loyalty", "purity")
labs <- c("moral", "care", "fairness", "authority", "loyalty", "purity")
preDobbs52Props <- rbind(moral_p_PRE52[c(2,1), c(1, 4)],
                         care_p_PRE52[c(2,1), c(1,4)], 
                         fair_p_PRE52[c(2,1), c(1,4)], 
                         aut_p_PRE52[c(2,1), c(1,4)], 
                         loyal_p_PRE52[c(2,1), c(1,4)], 
                         pur_p_PRE52[c(2,1), c(1,4)])
preDobbs52Props_2col <- round(cbind(preDobbs52Props[preDobbs52Props$pre52_Dobbs==1, 2],
                              preDobbs52Props[preDobbs52Props$pre52_Dobbs==0, 2]), 3)
dates <- c("(3/12/22-5/2/22)", "(5/22/2022-6/24/22)")
#preDobbs52Props_2col <- rbind(dates, preDobbs52Props_2col)
colnames(preDobbs52Props_2col) <- c("Before Dobbs Leak", "After Dobbs Leak")
rownames(preDobbs52Props_2col) <- labs
```


```{r include = FALSE}

postOV52Props <- rbind(moral_p_OV52[, c(1, 4)],
                         care_p_OV52[, c(1,4)], 
                         fair_p_OV52[,c(1,4)], 
                         aut_p_OV52[, c(1,4)], 
                         loyal_p_OV52[, c(1,4)], 
                         pur_p_OV52[, c(1,4)])
postOV52Props_2col <- round(cbind(postOV52Props[postOV52Props$post52_Overturn==1, 2],
                              postOV52Props[postOV52Props$post52_Overturn==0, 2]),3)
dates <- c("(3/12/22-6/24/22)", "(6/24/22-8/15/22)")
#postOV52Props_2col <- rbind(dates, (postOV52Props_2col))
colnames(postOV52Props_2col) <- c("Before Overturn", "After Overturn")
rownames(postOV52Props_2col) <- labs
```

```{r include = FALSE}
dates <- c("(1/1/22-6/24/22)", "(6/24/22-1/6/22)")
befOVProps <-rbind(moral_p_Bef[c(2,1), c(1, 4)],
                         care_p_Bef[c(2,1), c(1,4)], 
                         fair_p_Bef[c(2,1), c(1,4)], 
                         aut_p_Bef[c(2,1), c(1,4)], 
                         loyal_p_Bef[c(2,1), c(1,4)], 
                         pur_p_Bef[c(2,1), c(1,4)])
befOVProps_2col <- round(cbind(befOVProps[befOVProps$beforeOverturn==1, 2],
                              befOVProps[befOVProps$beforeOverturn==0, 2]),3)
colnames(postOV52Props_2col) <- c("Before Overturn*", "After Overturn*")
rownames(befOVProps_2col) <- labs
```

```{r echo=FALSE}
as.data.frame(cbind(preDobbs52Props_2col, 
                    postOV52Props_2col,
                    befOVProps_2col)) %>% kableExtra::kable()
```


## What is the moral makeup of abortion-related tweets published in 2022?

Within pro-life tweets, pro-choice tweets. neutral tweets, compute proportions


```{r warning=FALSE, message=FALSE}
dat$prolife_prochoice <- ordered(as.factor(dat$prolife_prochoice),
                                 c("life", "neutral", "choice"))
```

```{r warning=FALSE, message = FALSE}
# FAIRNESS 

# for pro-life tweets, look at the proportions across time points
 fair_p_life_pre52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(fairness)) %>%
  group_by(pre52_Dobbs, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(fairness==1)

fair_p_life_post52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(fairness)) %>%
  group_by(post52_Overturn, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(fairness==1)

 fair_p_life_bef<- dat %>% filter(prolife_prochoice=="life" & !is.na(fairness)) %>%
  group_by(beforeOverturn, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(fairness==1)
 
 fair_life_df <- round(rbind(t(fair_p_life_pre52[c(2,1),"prop"]),
                          t(fair_p_life_post52[,"prop"]),
                          t(fair_p_life_bef[c(2,1),"prop"])),3)
 labs2 <- c( "preDobbs52", "post overturn", "beforeOverturn") 
 labs <- c("pre", "post")
 rownames(fair_life_df) <- labs2
 colnames(fair_life_df) <- labs
 
 
 
 # for pro-choice tweets, look at the proportions across time points
 fair_p_choice_pre52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(fairness)) %>%
  group_by(pre52_Dobbs, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(fairness==1)

fair_p_choice_post52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(fairness)) %>%
  group_by(post52_Overturn, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(fairness==1)

 fair_p_choice_bef<- dat %>% filter(prolife_prochoice=="choice" & !is.na(fairness)) %>%
  group_by(beforeOverturn, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(fairness==1)
 
 fair_choice_df <- round(rbind(t(fair_p_choice_pre52[c(2,1),"prop"]),
                          t(fair_p_choice_post52[,"prop"]),
                          t(fair_p_choice_bef[c(2,1),"prop"])),3)

  # for ab neutral tweets, look at the proportions across time points
 fair_p_ab_neut_pre52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(fairness)) %>%
  group_by(pre52_Dobbs, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(fairness==1)

fair_p_ab_neut_post52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(fairness)) %>%
  group_by(post52_Overturn, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(fairness==1)

 fair_p_ab_neut_bef<- dat %>% filter(prolife_prochoice=="neutral" & !is.na(fairness)) %>%
  group_by(beforeOverturn, fairness) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(fairness==1)
 
 fair_ab_neut_df <- round(rbind(t(fair_p_ab_neut_pre52[c(2,1),"prop"]),
                          t(fair_p_ab_neut_post52[,"prop"]),
                          t(fair_p_ab_neut_bef[c(2,1),"prop"])),3)
 
 
 
 labs3 <- c("life","", "abortion neutral", "", "choice", "")
stance_fairness <- rbind(rep(labs,3), cbind(fair_life_df,fair_ab_neut_df,fair_choice_df))
  rownames(stance_fairness) <- c( "", "preDobbs52", "post overturn", "beforeOverturn") 
 colnames(stance_fairness) <- labs3
 
 stance_fairness %>% kableExtra::kable()
```

```{r}
# PURITY 

# for pro-life tweets, look at the proportions across time points
 purity_p_life_pre52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(purity)) %>%
  group_by(pre52_Dobbs, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(purity==1)

purity_p_life_post52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(purity)) %>%
  group_by(post52_Overturn, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(purity==1)

 purity_p_life_bef<- dat %>% filter(prolife_prochoice=="life" & !is.na(purity)) %>%
  group_by(beforeOverturn, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(purity==1)
 
 purity_life_df <- round(rbind(t(purity_p_life_pre52[c(2,1),"prop"]),
                          t(purity_p_life_post52[,"prop"]),
                          t(purity_p_life_bef[c(2,1),"prop"])),3)
 labs2 <- c( "preDobbs52", "post overturn", "beforeOverturn") 
 labs <- c("pre", "post")
 rownames(purity_life_df) <- labs2
 colnames(purity_life_df) <- labs
 
 
 
 # for pro-choice tweets, look at the proportions across time points
 purity_p_choice_pre52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(purity)) %>%
  group_by(pre52_Dobbs, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(purity==1)

purity_p_choice_post52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(purity)) %>%
  group_by(post52_Overturn, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(purity==1)

 purity_p_choice_bef<- dat %>% filter(prolife_prochoice=="choice" & !is.na(purity)) %>%
  group_by(beforeOverturn, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(purity==1)
 
 purity_choice_df <- round(rbind(t(purity_p_choice_pre52[c(2,1),"prop"]),
                          t(purity_p_choice_post52[,"prop"]),
                          t(purity_p_choice_bef[c(2,1),"prop"])),3)

  # for ab neutral tweets, look at the proportions across time points
 purity_p_ab_neut_pre52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(purity)) %>%
  group_by(pre52_Dobbs, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(purity==1)

purity_p_ab_neut_post52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(purity)) %>%
  group_by(post52_Overturn, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(purity==1)

 purity_p_ab_neut_bef<- dat %>% filter(prolife_prochoice=="neutral" & !is.na(purity)) %>%
  group_by(beforeOverturn, purity) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(purity==1)
 
 purity_ab_neut_df <- round(rbind(t(purity_p_ab_neut_pre52[c(2,1),"prop"]),
                          t(purity_p_ab_neut_post52[,"prop"]),
                          t(purity_p_ab_neut_bef[c(2,1),"prop"])),3)
 
 
 
 labs3 <- c("life","", "abortion neutral", "", "choice", "")
stance_purity <- rbind(rep(labs,3), cbind(purity_life_df,purity_ab_neut_df,purity_choice_df))
  rownames(stance_purity) <- c( "", "preDobbs52", "post overturn", "beforeOverturn") 
 colnames(stance_purity) <- labs3
 
 stance_purity %>% kableExtra::kable()
```



```{r warning=FALSE, message = FALSE}
# AUTHORITY

# for pro-life tweets, look at the proportions across time points
 fair_p_life_pre52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(authority)) %>%
  group_by(pre52_Dobbs, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(authority==1)

fair_p_life_post52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(authority)) %>%
  group_by(post52_Overturn, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(authority==1)

 fair_p_life_bef<- dat %>% filter(prolife_prochoice=="life" & !is.na(authority)) %>%
  group_by(beforeOverturn, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(authority==1)
 
 fair_life_df <- round(rbind(t(fair_p_life_pre52[c(2,1),"prop"]),
                          t(fair_p_life_post52[,"prop"]),
                          t(fair_p_life_bef[c(2,1),"prop"])),3)
 labs2 <- c( "preDobbs52", "post overturn", "beforeOverturn") 
 labs <- c("pre", "post")
 rownames(fair_life_df) <- labs2
 colnames(fair_life_df) <- labs
 
 
 
 # for pro-choice tweets, look at the proportions across time points
 fair_p_choice_pre52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(authority)) %>%
  group_by(pre52_Dobbs, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(authority==1)

fair_p_choice_post52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(authority)) %>%
  group_by(post52_Overturn, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(authority==1)

 fair_p_choice_bef<- dat %>% filter(prolife_prochoice=="choice" & !is.na(authority)) %>%
  group_by(beforeOverturn, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(authority==1)
 
 fair_choice_df <- round(rbind(t(fair_p_choice_pre52[c(2,1),"prop"]),
                          t(fair_p_choice_post52[,"prop"]),
                          t(fair_p_choice_bef[c(2,1),"prop"])),3)

  # for ab neutral tweets, look at the proportions across time points
 fair_p_ab_neut_pre52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(authority)) %>%
  group_by(pre52_Dobbs, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(authority==1)

fair_p_ab_neut_post52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(authority)) %>%
  group_by(post52_Overturn, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(authority==1)

 fair_p_ab_neut_bef<- dat %>% filter(prolife_prochoice=="neutral" & !is.na(authority)) %>%
  group_by(beforeOverturn, authority) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(authority==1)
 
 fair_ab_neut_df <- round(rbind(t(fair_p_ab_neut_pre52[c(2,1),"prop"]),
                          t(fair_p_ab_neut_post52[,"prop"]),
                          t(fair_p_ab_neut_bef[c(2,1),"prop"])),3)
 
 
 
 labs3 <- c("life","", "abortion neutral", "", "choice", "")
stance_authority <- rbind(rep(labs,3), cbind(fair_life_df,fair_ab_neut_df,fair_choice_df))
  rownames(stance_authority) <- c( "", "preDobbs52", "post overturn", "beforeOverturn") 
 colnames(stance_authority) <- labs3
 
 stance_authority %>% kableExtra::kable()
```




```{r warning=FALSE, message = FALSE}
# LOYALTY

# for pro-life tweets, look at the proportions across time points
 loyalty_p_life_pre52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(loyalty)) %>%
  group_by(pre52_Dobbs, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(loyalty==1)

loyalty_p_life_post52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(loyalty)) %>%
  group_by(post52_Overturn, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(loyalty==1)

 loyalty_p_life_bef<- dat %>% filter(prolife_prochoice=="life" & !is.na(loyalty)) %>%
  group_by(beforeOverturn, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(loyalty==1)
 
 loyalty_life_df <- round(rbind(t(loyalty_p_life_pre52[c(2,1),"prop"]),
                          t(loyalty_p_life_post52[,"prop"]),
                          t(loyalty_p_life_bef[c(2,1),"prop"])),3)
 labs2 <- c( "preDobbs52", "post overturn", "beforeOverturn") 
 labs <- c("pre", "post")
 rownames(loyalty_life_df) <- labs2
 colnames(loyalty_life_df) <- labs
 
 
 
 # for pro-choice tweets, look at the proportions across time points
 loyalty_p_choice_pre52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(loyalty)) %>%
  group_by(pre52_Dobbs, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(loyalty==1)

loyalty_p_choice_post52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(loyalty)) %>%
  group_by(post52_Overturn, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(loyalty==1)

 loyalty_p_choice_bef<- dat %>% filter(prolife_prochoice=="choice" & !is.na(loyalty)) %>%
  group_by(beforeOverturn, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(loyalty==1)
 
 loyalty_choice_df <- round(rbind(t(loyalty_p_choice_pre52[c(2,1),"prop"]),
                          t(loyalty_p_choice_post52[,"prop"]),
                          t(loyalty_p_choice_bef[c(2,1),"prop"])),3)

  # for ab neutral tweets, look at the proportions across time points
 loyalty_p_ab_neut_pre52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(loyalty)) %>%
  group_by(pre52_Dobbs, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(loyalty==1)

loyalty_p_ab_neut_post52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(loyalty)) %>%
  group_by(post52_Overturn, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(loyalty==1)

 loyalty_p_ab_neut_bef<- dat %>% filter(prolife_prochoice=="neutral" & !is.na(loyalty)) %>%
  group_by(beforeOverturn, loyalty) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(loyalty==1)
 
 loyalty_ab_neut_df <- round(rbind(t(loyalty_p_ab_neut_pre52[c(2,1),"prop"]),
                          t(loyalty_p_ab_neut_post52[,"prop"]),
                          t(loyalty_p_ab_neut_bef[c(2,1),"prop"])),3)
 
 
 
 labs3 <- c("life","", "abortion neutral", "", "choice", "")
stance_loyalty <- rbind(rep(labs,3), cbind(loyalty_life_df,loyalty_ab_neut_df,loyalty_choice_df))
  rownames(stance_loyalty) <- c( "", "preDobbs52", "post overturn", "beforeOverturn") 
 colnames(stance_loyalty) <- labs3
 
 stance_loyalty %>% kableExtra::kable()
```



```{r warning=FALSE, message = FALSE}
# CARE

# for pro-life tweets, look at the proportions across time points
 care_p_life_pre52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(care)) %>%
  group_by(pre52_Dobbs, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(care==1)

care_p_life_post52 <- dat %>% filter(prolife_prochoice=="life" & !is.na(care)) %>%
  group_by(post52_Overturn, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(care==1)

 care_p_life_bef<- dat %>% filter(prolife_prochoice=="life" & !is.na(care)) %>%
  group_by(beforeOverturn, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(care==1)
 
 care_life_df <- round(rbind(t(care_p_life_pre52[c(2,1),"prop"]),
                          t(care_p_life_post52[,"prop"]),
                          t(care_p_life_bef[c(2,1),"prop"])),3)
 labs2 <- c( "preDobbs52", "post overturn", "beforeOverturn") 
 labs <- c("pre", "post")
 rownames(care_life_df) <- labs2
 colnames(care_life_df) <- labs
 
 
 
 # for pro-choice tweets, look at the proportions across time points
 care_p_choice_pre52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(care)) %>%
  group_by(pre52_Dobbs, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(care==1)

care_p_choice_post52 <- dat %>% filter(prolife_prochoice=="choice" & !is.na(care)) %>%
  group_by(post52_Overturn, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(care==1)

 care_p_choice_bef<- dat %>% filter(prolife_prochoice=="choice" & !is.na(care)) %>%
  group_by(beforeOverturn, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(care==1)
 
 care_choice_df <- round(rbind(t(care_p_choice_pre52[c(2,1),"prop"]),
                          t(care_p_choice_post52[,"prop"]),
                          t(care_p_choice_bef[c(2,1),"prop"])),3)

  # for ab neutral tweets, look at the proportions across time points
 care_p_ab_neut_pre52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(care)) %>%
  group_by(pre52_Dobbs, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(care==1)

care_p_ab_neut_post52 <- dat %>% filter(prolife_prochoice=="neutral" & !is.na(care)) %>%
  group_by(post52_Overturn, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n))%>% filter(care==1)

 care_p_ab_neut_bef<- dat %>% filter(prolife_prochoice=="neutral" & !is.na(care)) %>%
  group_by(beforeOverturn, care) %>%
  summarise(n = n()) %>% mutate(prop = n/sum(n)) %>% filter(care==1)
 
 care_ab_neut_df <- round(rbind(t(care_p_ab_neut_pre52[c(2,1),"prop"]),
                          t(care_p_ab_neut_post52[,"prop"]),
                          t(care_p_ab_neut_bef[c(2,1),"prop"])),3)
 
 
 
 labs3 <- c("life","", "abortion neutral", "", "choice", "")
stance_care <- rbind(rep(labs,3), cbind(care_life_df,care_ab_neut_df,care_choice_df))
  rownames(stance_care) <- c( "", "preDobbs52", "post overturn", "beforeOverturn") 
 colnames(stance_care) <- labs3
 
 stance_care %>% kableExtra::kable()
```


```{r}
df <- as.data.frame(rbind(stance_care, stance_fairness, 
                          stance_authority, stance_loyalty, stance_purity))
df %>% kableExtra::kable()

```



```{r}

```






- pre52Dobbs (1 -> 0)
- post52Overturn (0 -> 1)
- beforeOverturn (1 -> 0)

note - pre52Dobbs,post52Overturn 52 days compared to 104
